Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-06-08 Ben_Manuscripts/structure_paper/Draft.tex
Draft updates + PMF stuff

  \begin{figure}[!htb]
  \centering
  %BJC4: I could cut out the tails in the three real space configurations
  %BJC4: I can remove some of the colorbars and state that they all follow the same color bar. 
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
	\label{fig:rotated_carboxylate}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.png}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.png}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
  	\label{fig:rotated_carboxylate_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
  	%BJC4: needs to run longer
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png}
  	\caption{}\label{fig:staggered_rzplot_norestraints}
  	%BJC4: needs to be done
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \caption{R-double is present in all three inital configurations tested while the heavy atoms
  in the headgroup are held in place with position restraints. R-double fades once 
  the position restriants are released.}\label{fig:rdouble}
  \end{figure}

@@

  The addition of water allows R-double to appear. When we add 1 wt\% water to the 
  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
  of the parallel displaced configuration become more diffuse, which is a closer match to 
  experiment. If water is truly responsible for R-double, then the there is likely
  between 1 and 2.5 wt\% water absorbed into the membrane. This does not exclude 
  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
  may facilitate the stability of such motifs. 
%  However, given the long-term stability of this configuration, it is most likely that small
%  amounts of water are responsible for the existence of R-double.

@@

  Water causes the monomer head groups to restructure. We confirmed that the reflection is 
  not caused by the water itself. We removed all water molecules from the trajectory and 
  showed that R-double is still present in the simulated diffraction pattern 
  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
  R-double. R-double is not present when we remove all atoms except carbon atoms that make
  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
  and head groups causes them to restructure in a way that leads to R-double.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
  \caption{Full system}\label{fig:rdouble_offset}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{rdouble_nowater_rzplot.png}
  \caption{Water removed}\label{fig:rdouble_nowater}
  \end{subfigure}
  \begin{subfigure}{0.32\textwidth}
  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
  \caption{Tails only}\label{fig:rdouble_tails}
  \end{subfigure}
  \caption{The structure of the head groups is responsible for the appearance of
  R-double in (a). Removing water from the trajectory (b) results in a simulated 
  diffraction pattern nearly identical to that in (a). R-double is not present
  when we simulate the diffraction pattern of system where only tails are present. 
  (c)}\label{fig:rdouble_origin}
  \end{figure}

  The appearance of R-double may be due to increased order of the pores. The first
  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
  Based on the peak locations, it is evident that the head groups stack closer 
  together in the solvated configuration which may play a role in enforcing order.
  This may be in part due to swelling of the pores. In 
  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
  head group density within 0.4 nm of the pore center. Water molecules may swell 
  the pores and hydrogen bond with monomer head groups, tethering the monomers 
  closer together. If this is the case, then it implies that R-double has always
  been at least weakly present in the simulated diffraction patterns, but may 
  have been buried by noise.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
  \caption{}\label{fig:solvated_correlation_overlay}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
  \caption{}\label{fig:head_group_density_overlay}
  \end{subfigure}
  \caption{}\label{fig:rdouble_structuring}
  \end{figure}

@@

  %BJC5: probably should show solvated system measurements
  % 1 wt % water, parallel displaced, ordered basin
  % Nernst Einstein : (6.52 +/- 0.04) e-05 S/m
  % Collective Diffusion : (20.6 +/- 9.8) e-05 S/m

>>>>

  \begin{figure}[!htb]
  \centering
  %BJC4: I could cut out the tails in the three real space configurations
  %BJC4: I can remove some of the colorbars and state that they all follow the same color bar. 
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate.png}
	\label{fig:rotated_carboxylate}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered.png}
	\label{fig:staggered}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers.png}
  	\label{fig:rotated_monomers}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_restrained.png}
  	\label{fig:rotated_carboxylate_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_restrained.png}
  	\label{fig:staggered_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_restrained.png}
  	\label{fig:rotated_monomers_rzplot_restrained}
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_carboxylate_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_carboxylate_rzplot_norestraints}
  	%BJC4: needs to run longer
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{staggered_rzplot_norestraints.png} %BJC5: this needs to be updated
  	\caption{}\label{fig:staggered_rzplot_norestraints} 
  \end{subfigure}
  \begin{subfigure}{0.3\linewidth}
  	\centering
  	\includegraphics[width=\textwidth]{rotated_monomers_rzplot_norestraints.png}
  	\caption{}\label{fig:rotated_monomers_rzplot_norestraints}
  \end{subfigure}
  \caption{R-double is present in all three inital configurations tested while the heavy atoms
  in the headgroup are held in place with position restraints. R-double fades once 
  the position restriants are released.}\label{fig:rdouble}
  \end{figure}

@@

  The addition of water allows R-double to appear. When we add 1 wt\% water to the 
  parallel displaced configuration, R-double becomes visible (Figure~\ref{fig:rdouble_offset}). 
  When 2.5 wt\% water is added, R-double disappears, but the helical reflections characteristic
  of the parallel displaced configuration become more diffuse, which is a closer match to 
  experiment. If water is truly responsible for R-double, then there is likely
  between 1 and 2.5 wt\% water absorbed into the membrane. This does not exclude 
  possible contributions from the motifs discussed in section~\ref{section:rdouble}. Water
  may facilitate the stability of such motifs. 
%  However, given the long-term stability of this configuration, it is most likely that small
%  amounts of water are responsible for the existence of R-double.

@@

  R-double appears due to the structure of the head groups. We removed the head groups from the
  trajectory used to produce Figure~\ref{fig:solvation}a in order to produce that shown
  in Figure~\ref{fig:rdouble_nophenyls}. R-double does not appear without the influence of the
  head groups. Water molecules must play a role in the structuring of the head groups since 
  R-double does not appear in any dry simulations.

%  Water causes the monomer head groups to restructure.   
%  We confirmed that the reflection is 
%  not caused by the water itself. We removed all water molecules from the trajectory and 
%  showed that R-double is still present in the simulated diffraction pattern 
%  (Figure~\ref{fig:rdouble_nowater}). We also confirmed that the tails are not responsible for
%  R-double. R-double is not present when we remove all atoms except carbon atoms that make
%  up the tails (Figure~\ref{fig:rdouble_tails}). It is clear that interactions between water
%  and head groups causes them to restructure in a way that leads to R-double.

  % BJC5: This figure may belong in supplemental
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{rdouble_offset_solvated_rzplot.png}
  \caption{Full system}\label{fig:rdouble_offset}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{nophenyls_rzplot.png}
  \caption{Head groups removed}\label{fig:rdouble_nophenyls}
  \end{subfigure}
%  \begin{subfigure}{0.32\textwidth}
%  \includegraphics[width=\textwidth]{rdouble_tails_only_rzplot.png}
%  \caption{Tails only}\label{fig:rdouble_tails}
%  \end{subfigure}
  \caption{The structure of the head groups is responsible for the appearance of
  R-double in (a). Removing head groups from the trajectory results in a simulated 
  diffraction pattern that does not show R-double (b)}\label{fig:rdouble_origin}
  \end{figure}

  When two vertically stacked monomer head groups hydrogen bond with a shared water 
  molecule, the monomers are drawn closer together (as illustrated in 
  Figure~\ref{fig:hbond_visualization}), which creates an asymmetry that allows 
  R-double to appear. If a monomer head group shares a hydrogen bonded water molecule
  with a head group below itself, it will be less likely to share a water molecule 
  with a head group above it due to steric constraints. The monomer head group above
  can just as easily share a water molecule with a head group above itself. In this scenario,
  the centers of each group are 2 times the $\pi$-stacking distance apart which would
  lead to R-double (much like the configuration in Figure~\ref{fig:staggered}). There are
  a modest number of occurences of this scenario, shown in Figure~\ref{fig:pore_hbonds}. 
  Peaks in the distributions represent the scenario where a monomer head group shares a 
  water molecule with a head group vertically above it. In Figure~\ref{fig:pore_hbonds_ft},
  we calculated the discrete fourier transform of the distributions which we used as a rough 
  indicator of whether the head group arrangement will lead to R-double. We see the 
  strongest indicator of asymmetric monomer stacking in Pore 1 where the peaks at 0.5
  layers$^{-1}$ are clearly distinguished, meaning there is periodicity every two layers.

  \begin{figure}[!htb]
  \centering
  % BJC5: alt figure : hbonds_tails.png (a little more crowded, but gives more context
  % to the floating head groups)
  \includegraphics[width=0.5\textwidth]{hbonds_notails.png}
  \caption{Monomer head groups that hydrogen bond with a shared water molecule are 
  drawn closer together. Head groups with blue bonds were stacked above those 
  with orange bonds in the initial configuration.}\label{fig:hbond_visualization}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds.png}
  \caption{}\label{fig:pore_hbonds}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
  \includegraphics[width=\textwidth]{pore_hbonds_ft.png}
  \caption{}\label{fig:pore_hbonds_ft}
  \end{subfigure}
  \caption{(a) The average number of interlayer hydrogen bonds. Peaks indicate a 
  shared hydrogen bonded water molecule between a monomer head group and that stacked
  vertically above it. (b) }\label{fig:hbond_quantification}
  \end{figure}

%  The appearance of R-double may be due to increased order of the pores. The first
%  peak of the correlation function, $g(z)$, is approximately 30 \% larger in the 
%  solvated versus dry configuration (Figure~\ref{fig:solvated_correlation_overlay}).
%  Based on the peak locations, it is evident that the head groups stack closer 
%  together in the solvated configuration which may play a role in enforcing order.
%  This may be in part due to swelling of the pores. In 
%  Figure~\ref{fig:head_group_density_overlay} there is a clear decrease in 
%  head group density within 0.4 nm of the pore center. Water molecules may swell 
%  the pores and hydrogen bond with monomer head groups, tethering the monomers 
%  closer together. If this is the case, then it implies that R-double has always
%  been at least weakly present in the simulated diffraction patterns, but may 
%  have been buried by noise.
% 
%  \begin{figure}[!htb]
%  \centering
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{solvated_correlation_overlay.png}
%  \caption{}\label{fig:solvated_correlation_overlay}
%  \end{subfigure}
%  \begin{subfigure}{0.45\textwidth}
%  \includegraphics[width=\textwidth]{head_group_density_overlay.png}
%  \caption{}\label{fig:head_group_density_overlay}
%  \end{subfigure}
%  \caption{}\label{fig:rdouble_structuring}
%  \end{figure}

@@

  %BJC5: which system should I study here? I wrote this before the solvated
  % system showed R-double. It might make sense to study the solvated system for ionic
  % conductivity and cross-linking.
